Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-05-28 paper/results.tex
Last
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@626 3fc257bb-8550-0410-81b3-a5c103da83f7

The execution times for the maximally independent set algorithm
(Figure~\ref{fig:luby}) are shown in Figure~\ref{f:luby}.  Like the R-MAT
generation results, superlinear speed-up of the algorithm occurs for RMAT-20
and RMAT-24, as more of the graph fits into processor memory and less file
I/O is needed.  For RMAT-28, the algorithm requires significant out-of-core
operations. In this case, parallel efficiency is nearly perfect going from 
8 to 32 processors; some loss of efficiency is seen at 64 processors,
where the parallel efficiency compared to the 8-processor case is KDD\%.

>>>>

The execution times for the maximally independent set algorithm
(Figure~\ref{fig:luby}) are shown in Figure~\ref{f:luby}.  Like the R-MAT
generation results, superlinear speed-up of the algorithm occurs for RMAT-20
and RMAT-24, as more of the graph fits into processor memory and less file
I/O is needed.  For RMAT-28, the algorithm requires significant out-of-core
operations. In this case, parallel efficiency is nearly perfect going from 
8 to 32 processors; some loss of efficiency is seen at 64 processors,
where the parallel efficiency compared to the 8-processor case is 69\%.
